Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-02 Dissertation/Thesis/tex/ae2D.tex
updated figs of chap 5
updated references of myself

In this section, we define Shannon's entropy as a measure of map uncertainty, and present a novel approach to predict future entropy from an arbitrary ray. Then we discuss computational modifications for real-time implementation.

@@

\begin{figure}
\vspace*{0.1\columnwidth}
\centerline{
	\includegraphics[height=0.35\columnwidth]{ExampleOptimalPose.png}
}
\begin{picture}(0,0)(0,0)
\setlength{\unitlength}{0.1\columnwidth}\scriptsize
\put(4.4,2.1){\color{blue}$X_t$}
\put(5.9,1.9){\color{red}$x_1$}
\put(2.9,2.0){\color{red}$x_5$}
\put(4.4,3.6){\color{red}$x_3$}
\put(4.4,0.6){\color{red}$x_7$}
\put(5.4,3.0){\color{red}$x_2$}
\put(3.3,3.1){\color{red}$x_4$}
\put(3.3,1.0){\color{red}$x_6$}
\put(5.4,1.0){\color{red}$x_8$}
\put(6.8,3.1){\color{red}$z_{2,1}$}
\put(4.5,3.1){\color{red}$z_{2,5}$}
\put(5.6,4.1){\color{red}$z_{2,3}$}
\put(5.6,2.2){\color{red}$z_{2,7}$}
\put(6.5,3.7){\color{red}$z_{2,2}$}
\put(4.9,3.8){\color{red}$z_{2,4}$}
\put(5.0,2.5){\color{red}$z_{2,6}$}
\put(6.5,2.5){\color{red}$z_{2,8}$}
\put(6.1,2.9){$X_c^*$}
\end{picture}
\caption{Optimal Pose Selection Illustration
}
	\medskip
	\small
	This figure illustrates the expanding ring method. Initially, a robot (blue circle) views down and left (blue sector). Then, the robot considers $n_c=8$ poses (red circles) as possible candidates for where to move next. For each candidate, $n_d=8$ directions are considered (red lines, only displayed on candidate location $c=2$). Then, the expected entropy of each ray is calculated. The scan (red sector) covering those rays with the largest expected entropy decrease is chosen for each candidate, and the best candidate $X_c^*$ (black circle: location, black sector: scan) is chosen to maximize information gain. Finally, Dijkstra's algorithm provides the collision-free motion between $X_t$ and $X_c^*$, and the process is repeated.
\label{fig:OptProcess}
\end{figure}

>>>>

In this section, we define Shannon's entropy as a measure of map uncertainty, and present a novel approach to predict future entropy from an arbitrary ray~\cite{KauAiLee16}. Then we discuss computational modifications for real-time implementation.

@@

\begin{figure}
\vspace*{0.1\columnwidth}
\centerline{
	\includegraphics[height=0.35\columnwidth]{ExampleOptimalPose.png}
}
\begin{picture}(0,0)(0,0)
\setlength{\unitlength}{0.1\columnwidth}\scriptsize
\put(4.4,2.1){\color{blue}$X_t$}
\put(5.9,1.9){\color{red}$x_1$}
\put(2.9,2.0){\color{red}$x_5$}
\put(4.4,3.6){\color{red}$x_3$}
\put(4.4,0.6){\color{red}$x_7$}
\put(5.4,3.0){\color{red}$x_2$}
\put(3.3,3.1){\color{red}$x_4$}
\put(3.3,1.0){\color{red}$x_6$}
\put(5.4,1.0){\color{red}$x_8$}
\put(6.8,3.1){\color{red}$z_{2,1}$}
\put(4.5,3.1){\color{red}$z_{2,5}$}
\put(5.6,4.1){\color{red}$z_{2,3}$}
\put(5.6,2.2){\color{red}$z_{2,7}$}
\put(6.5,3.7){\color{red}$z_{2,2}$}
\put(4.9,3.8){\color{red}$z_{2,4}$}
\put(5.0,2.5){\color{red}$z_{2,6}$}
\put(6.5,2.5){\color{red}$z_{2,8}$}
\put(6.1,2.9){$X_c^*$}
\end{picture}
\caption{Optimal Pose Selection Illustration
}
\centering{
	\medskip
	\small
	This figure illustrates the expanding ring method. Initially, a robot (blue circle) views down and left (blue sector). Then, the robot considers $n_c=8$ poses (red circles) as possible candidates for where to move next. For each candidate, $n_d=8$ directions are considered (red lines, only displayed on candidate location $c=2$). Then, the expected entropy of each ray is calculated. The scan (red sector) covering those rays with the largest expected entropy decrease is chosen for each candidate, and the best candidate $X_c^*$ (black circle: location, black sector: scan) is chosen to maximize information gain. Finally, Dijkstra's algorithm provides the collision-free motion between $X_t$ and $X_c^*$, and the process is repeated.
}
\label{fig:OptProcess}
\end{figure}
